### 2019-12-28 interim/sections/background/scribble.tex
Update .bib for papers read
Interim write-up:  binary session types
Interim write-up:  start on Scribble

\subsection{Overview}
\begin{itemize}
\item Introduce Scribble language as implementation of MPST
\end{itemize}

\subsection{Protocol Specification}
\begin{itemize}
\item Show parallels between Scribble protocol and MPST global type
\end{itemize}

@@

\mathbb{T} ::= & \tt{int},~\tt{bool},~T,~T',~\dots & \text{Payload Format Types} \\

>>>>

\subsection{Overview}
% Introduce Scribble as an implementation of MPST

% Protocol specification: show parallels between Scribble protocol and MPST global type

\begin{lstlisting}[language=Java,numbers=left,frame=single]
// TODO: Adder Protocol
\end{lstlisting}

\[
\begin{array}{rl}
G = \mu\mathbf{t}.\parti{Client}\to\parti{Server}:\{
& \text{Add}(\texttt{int}, \texttt{int}): \parti{Server}\to\parti{Client}: \{\text{Res}(\texttt{int}): \mathbf{t}\}, \\
& \text{Quit}(): \parti{Server}\to\parti{Client}: \{\text{Terminate}(): \mathbf{end}\}\\
\} &
\end{array}
\]

@@

\mathbb{T} ::= & \texttt{int},~\texttt{bool},~T,~T',~\dots & \text{Payload Format Types} \\
